---
title: "Mutton Flavour Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Week 3 - Data Visualisation Exercise 1. 

##Prepared by Loretta Clancy

###Background Information

Fatty acids including MOA, EOA and MNA accumulate in lamb meat and can make meat from older animals taste unpleasant. Another fatty acid, C17:0, also accumlates with age although is not responsible for the unpleasant 'mutton flavour'. C17 is easier to measure than MOA, EOA or MNA; this study investigates whether C17 could be a useful 'proxy' for indicating how 'muttony' meat is likely to taste. 


```{r include=FALSE}
library(tidyverse)

flavourData <- read_csv("../rawData/bcfa_C17_fa.csv")
```

<br>
```{r,  echo=FALSE, results='hide', fig.keep='all'}
flavourData %>% tidyr::gather("FattyAcid", "value", 1:3) %>% 
  ggplot(., aes(C17.0, value, shape=as.factor(Year), colour=FattyAcid)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE, colour="black") +
  labs(title="Investigate relationship between C17.0 against other Fatty Acids", y="", shape="Year", colour="Fatty Acid") +
  facet_wrap(~FattyAcid)

```
