---
title: "Mutton Flavour Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Week 3 - Data Visualisation Exercise 1. 

##Prepared by Loretta Clancy

###Background Information

Fatty acids including MOA, EOA and MNA accumulate in lamb meat and can make meat from older animals taste unpleasant. Another fatty acid, C17:0, also accumlates with age although is not responsible for the unpleasant 'mutton flavour'. C17 is easier to measure than MOA, EOA or MNA; this study investigates whether C17 could be a useful 'proxy' for indicating how 'muttony' meat is likely to taste. 

**NOTE:** Data will need to be downloaded from https://confluence.csiro.au/download/attachments/571015571/bcfa_C17_fa.csv?version=1&modificationDate=1521545267220&api=v2 and should be placed into the rawData directory for this project.



###Processes



Add the required libraries
```{r echo=FALSE}
library(tidyverse)
```

Import the data

```{r }
flavourData <- read_csv("../rawData/bcfa_C17_fa.csv")
```

View the data
```{r }
str(flavourData)
head(flavourData)
```

###Visualising the data
In this instance I want to see how the fatty acid levels compare within each sample.  To do this, I will need to add an observation Id (obsId) and then tidy the data

```{r }
tidyFlavour <- flavourData %>% 
  mutate(obsId = 1:n()) %>% 
  gather("FattyAcids", "value", 1:4)
tidyFlavour
```

And now we can plot the data.  This will be a large (horizontal) chart

```{r }
ggplot(tidyFlavour, aes(x=obsId, y=value, colour=FattyAcids)) +
  geom_point()
```

#Observation regarding this data:
MOA observations are very diverse, with some really high values, not sure if this indicates an issue with the observations or not
C17.0 is, in most instances the lowest value, but not always, not sure if this indicates an issue with the observations or not
Do we get a different picture if we filter by the year

```{r }
ggplot(tidyFlavour, aes(x=obsId, y=value, colour=FattyAcids)) +
  geom_point() +
  facet_grid(Year ~ .)
```

This shows a lot of samples in 2011, but very few in 2014.  Lets look of the 'make up' of the data.

```{r }
tidyFlavour %>% count(Year)
flavourData %>% count(MOA > MNA)
flavourData %>% count(MNA > EOA)
flavourData %>% count(EOA > C17.0)
```

I would question the validity of the samples where EOA is less than C17.0.  Now to look at the distribution of the values

```{r }
ggplot(tidyFlavour, aes(x=FattyAcids, y=value)) +
  geom_boxplot() +
  facet_grid(~Year)

```

This supports the graph displayed above. But it does not show any indication of the sample sizes.  Now I will compare the variables against each other

```{r }
ggplot(flavourData, aes(x=MOA, y=C17.0, shape=as.factor(Year))) +
  geom_point() + 
  geom_smooth(method='lm', se=FALSE) 

ggplot(flavourData, aes(x=MNA, y=C17.0, shape=as.factor(Year))) +
  geom_point() + 
  geom_smooth(method='lm', se=FALSE) 

ggplot(flavourData, aes(x=EOA, y=C17.0, shape=as.factor(Year))) +
  geom_point() + 
  geom_smooth(method='lm', se=FALSE) 

```

There seams to be a considerable discrepancy in the relationship between the different sample years.

Lets look at this a different way

```{r }
flavourData %>% tidyr::gather("FattyAcid", "value", 1:3) %>% 
  ggplot(., aes(C17.0, value, shape=as.factor(Year), colour=FattyAcid)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE, colour="black") +
  labs(title="Investigate relationship between C17.0 against other Fatty Acids", y="", shape="Year", colour="Fatty Acid") +
  facet_wrap(~FattyAcid)

```

We will have a look at the individual stats to see if they provide any assistance ... will need "broom" package for this.

```{r }
library(broom)
```


```{r include=FALSE }
fit_C17.0_MOA <- lm(C17.0 ~ MOA, data=flavourData)
summary(fit_C17.0_MOA)
tidy_fit_C17.0_MOA <- tidy(fit_C17.0_MOA) %>% 
  filter(term == "MOA")

fit_C17.0_MNA <- lm(C17.0 ~ MNA, data=flavourData)
summary(fit_C17.0_MNA)
tidy_fit_C17.0_MNA <- tidy(fit_C17.0_MNA) %>% 
  filter(term == "MNA")

fit_C17.0_EOA <- lm(C17.0 ~ EOA, data=flavourData)
summary(fit_C17.0_EOA)
tidy_fit_C17.0_EOA <- tidy(fit_C17.0_EOA) %>% 
  filter(term == "EOA")

tidyStats <- rbind(tidy_fit_C17.0_MOA, tidy_fit_C17.0_MNA,  tidy_fit_C17.0_EOA)
```

```{r }
tidyStats

```

The above shows the stats for each Fatty Acid agains the C17.0 Fatty Acid overall.  However, I think further investigation needs to be done regard the clear differences between the years. 
<br>
<br>




