---
title: "Mutton Flavour Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Week 3 - Data Visualisation Exercise 1. 

# Background Information

Fatty acids including MOA, EOA and MNA accumulate in lamb meat and can make meat from older animals taste unpleasant. Another fatty acid, C17:0, also accumlates with age although is not responsible for the unpleasant 'mutton flavour'. C17 is easier to measure than MOA, EOA or MNA; this study investigates whether C17 could be a useful 'proxy' for indicating how 'muttony' meat is likely to taste. 


#Processes

1. Add the required libraries
```{r echo=FALSE}
library(tidyverse)
```

2. Import the data

```{r echo=FALSE}
flavourData <- read_csv("../rawData/bcfa_C17_fa.csv")
```

3. View the data
```{r echo=FALSE}
str(flavourData)
head(flavourData)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
